Historical trends in the contribution of six major causes of death to the black-white life expectancy gap by US state

### 2017-04-07 Manuscript/Manuscript_COD_Trends.Rmd
AOC results

@@

**Figure 14: Smoothed state-level trends in the contribution of all other causes to the life expectancy gap vs. the overall pattern in males**

>>>>

**All other causes**

Mortality from all other causes generally decreased earlier in the time period, especially among blacks. White men and women have shown increasing mortality rates from all other causes since the 1980s, along with black women, while black men have continued to experience decreasing rates within several states. As such, the contribution of all other causes to the life expectancy gap has generally decreased over time, and reached equality in New York, Massachusettes, and Rhode Island for both genders (**Figures 13 and 14**). The most disparate states include Pennsylvania and DC, with much larger contributions estimated for all other causes in the earlier years within Pennsylvania and in the later years within DC.

@@

**Figure 14: Smoothed state-level trends in the contribution of all other causes to the life expectancy gap vs. the overall pattern in females**
